Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
color

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor} % colors
\newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
\newcommand{\hh}[1]{{\textcolor{Green}{#1}}}
\templatetype{pnasbriefreport} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report\citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly} \svp{sliding} \hh{one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and} \svp{keeping} \hh{track of the similarity measure.}

>>>>

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
\usepackage{cleveref}
\usepackage[dvipsnames]{xcolor} % colors
\newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
\newcommand{\hh}[1]{{\textcolor{ForestGreen}{#1}}}
\templatetype{pnasbriefreport} % Choose template
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report\citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly to slide one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and keep track of the similarity measure.}
